%----------------------------------------------------------------------------------------
%	CONTACT SECTION
%----------------------------------------------------------------------------------------
\name{Adrian Wei}
\contact{hanningwei92@gmail.com}{linkedin.com/in/hanning-wei-92312423a22f}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
	\textbf{University of Western Ontario} \hfill London, ON \\
	Bachelor of Engineering in Software Engineering \hfill Expected May 2027 \\
	\textit{Highlights: Varsity Table Tennis MVP, Relevant Coursework: Algorithms, Network Security, DBMS}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

	\textbf{Backend Developer} \hfill Dec 2025 – Present \\
	LeakSight (Western Cyber Society) \hfill Hybrid
	\begin{itemize}
		\item Tech Stack: Python, ML, Side-Channel Research
		\item Developing backend services for cybersecurity research tools.
	\end{itemize}

	\textbf{Software Developer} \hfill Nov 2025 – Present \\
	NCTTA \hfill Remote
	\begin{itemize}
		\item Tech Stack: C\#, .NET Core, SQL, MVC
		\item Building league management software for collegiate table tennis.
	\end{itemize}

	\textbf{Software Engineer Intern} \hfill Sept 2023 – Dec 2023 \\
	Match \hfill Remote
	\begin{itemize}
		\item Tech Stack: C++, Python, Linux
		\item Contributed to core matching algorithms and system optimization.
	\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects}

	\textbf{GitNest (SACHacks)} \hfill Python, Gemini AI \\
	AI-powered developer tool.

	\textbf{XR-848} \hfill C\#, Unity, Git \\
	Virtual reality experience.

	\textbf{NBA Predictive Analytics Model} \hfill Google Sheets, Apps Script \\
	Data analysis tool for sports predictions.

	\textbf{AeroDB} \hfill SQL, AWS, JavaScript \\
	Cloud-based database management system.

	\textbf{Secure Course Management System} \hfill Node.js, Express \\
	Secure web application for educational institutions.

	\textbf{MiniNet DNS Simulation} \hfill MiniNet, Linux, DNS \\
	Network security simulation project.

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
	\textbf{Languages}: Python, JavaScript, C++, C\#, Java, SQL, HTML/CSS, C \\
	\textbf{Frameworks}: .NET Core, MVC, React, Node.js, Express, Flask, TensorFlow, PyTorch, Gemini AI API \\
	\textbf{Tools}: Git/GitHub, Linux/UNIX, MiniNet, AWS, Azure, CI/CD, Docker
\end{rSection}
